I can see clearly now: reinterpreting statistical significance

### 2018-05-15 doc.tex
two small comments in the abstract

\textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''. commonly uis not about  whatever the use of have led to debates over whether to abandon its use. 
Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g. whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.

>>>>

\textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
We believe that a significant \mk{change word?} part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''. \mk{Broken sentence:} commonly uis not about  whatever the use of have led to debates over whether to abandon its use. 
Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g. whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.
